Interisland movements of woodland caribou in Newfoundland

### 2020-02-21 paper/manuscript.Rmd
forage limitation

## Forage limitation
Forage limitation and over-grazing is a major concern for caribou populations
[@Schaefer_2016] and could explain movement between
islands. Conspecific competition for resources driven by reduced foraging
opportunities can decrease reproductive success of adult females [@Schaefer_2016]. Forage scarcity has been proposed as a potential reason for caribou
moving between arctic islands on the sea-ice in winter [@Miller_1977].
For very small islands, over-grazing by newly arrived caribou may rapidly
deplete forage [@Bergerud_1990]. Without sea ice, movement from the
mainland to an island, or between islands, requires caribou to assess the
trade-off associated with swimming.

This trade-off can be understood as density-dependent habitat selection governed
by the Ideal Free Distribution [@Morris_1987; @Bradbury_2015]. Ideal Free
Distribution theory predicts a fitness equilibrium: when the density in a given
habitat patch has exceeded the optimum for fitness within that patch, animals
should relocate and settle new habitat patches, so that fitness is equal across
all patches (Bradbury et al. 2015). Islands act as discrete habitat patches in
this case, but the costs associated with swimming create a trade-off when moving
between patches. For caribou in the Fogo Island archipelago, the role of forage
limitation in animal habitat selection patterns and movement remains unknown,
but swimming between islands may in part be explained by forage limitation and
conspecific competition.

>>>>

## Forage limitation
Forage limitation and over-grazing is a major concern for caribou populations
[@Schaefer_2015] and could explain movement between islands. Conspecific
competition for resources driven by reduced foraging opportunities can decrease
reproductive success of adult females [@Schaefer_2015]. Forage scarcity has been
proposed as a potential reason for caribou moving between arctic islands on the
sea-ice in winter [@Miller_1977]. For very small islands, over-grazing by newly
arrived caribou may rapidly deplete forage [@Bergerud_1990]. Without sea ice,
movement from the mainland to an island, or between islands, requires caribou to
assess the trade-off associated with swimming.

This trade-off can be understood as density-dependent habitat selection governed
by the Ideal Free Distribution [@Morris_1987; @Bradbury_2015]. Ideal Free
Distribution theory predicts a fitness equilibrium: when the density in a given
habitat patch has exceeded the optimum for fitness within that patch, animals
should relocate and settle new habitat patches, so that fitness is equal across
all patches [@Bradbury_2015]. Islands act as discrete habitat patches in
this case, but the costs associated with swimming create a trade-off when moving
between patches. For caribou in the Fogo Island archipelago, the role of forage
limitation in animal habitat selection patterns remains unknown,
but swimming between islands may in part be explained by forage limitation and
conspecific competition.
